---
title: "Final Production"
author: "Amber Thomas"
date: "1/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Every cell in this markdown file can be run to update the data in the web version of the dress codes story. 

```{r packages}
library(tidyverse)
library(here)
library(tools)
library(glue)
library(jsonlite)
```

## Importing Data

```{r}
source(here::here("r_scripts", "download_data.R"))
source(here::here("r_scripts", "other_limits.R"))
source(here::here("r_scripts", "length_limits.R"))
```

## Downloading the data

By running the `download_data.R` file, we automatically downloaded our data and created the dataframe `responses` which is filled with all of our manually-entered dress code data.

## Cleaning Data

First, we need to make our very wide data, long. 

```{r}
bannedBySchool <- findBanned(responses) %>% 
  select(c(School.Name, School.State.Abbreviation, prohibited, item, type)) %>% 
  filter(!grepl("exemptions", item)) %>%
  separate_rows(prohibited, sep = ", ") %>% 
  mutate(prohibited = trimws(prohibited), 
         prohibited = ifelse(prohibited == "NA" | prohibited == "na" | prohibited == "Na" | prohibited == "NA side slit", "none", prohibited)) %>% 
  filter(prohibited != "red and/or purple") %>% 
  mutate(prohibited = ifelse(prohibited == "boys", "male", prohibited))

```

The above data frame does not include things like length restrictions on pants/shorts/skirts, strap width restrictions, and promotion of various types of products/things on shirts. Let's analyze those here: 

### Length Restrictions

```{r}
length <- findLength(responses)
lengthBySchool <- length %>% 
  mutate(type = "length",
         limits = paste0("short ", limits)) %>% 
  rename(item = limits) %>% 
  select(-length) %>% 
  mutate(prohibited = NA_character_)

## For data repo - need to manually clean

write.csv(length, here::here("raw_data", "length_items.csv"), row.names = FALSE)

googledrive::drive_download("length_items", path = here::here("processed_data", "forRepo", "length_restrictions.csv"), type = "csv", overwrite = TRUE)

```

### Strap Restrictions

```{r}
strapLimits <- responses %>% 
  select(c("School.Name", "School.State.Abbreviation"), contains("shirt.straps")) %>% 
    rename(limits = !!names(.[3])) %>% 
    filter(limits != "") %>% 
    # Separate comma delimited list of items
    separate(limits, into = c("limits", "inches"), sep = ",") %>% 
    mutate(limits = trimws(limits),
           limits = gsub("(insert amount in other)", "", limits, fixed = TRUE),
           number = gsub('inch|inches|fingers|\\"|wide', "", inches)) %>% 
  select(-inches) 

strapsForRepo <- strapLimits %>% 
  rename(schoolName = School.Name, state = School.State.Abbreviation)

write.csv(strapsForRepo, here::here("processed_data", "forRepo", "strap_restrictions.csv"), row.names = FALSE)

straps <- strapLimits %>% 
    mutate(item = "narrow straps",
             type = "shirt") %>% 
  select(c("School.Name", "School.State.Abbreviation", "item", "type")) %>% 
  mutate(prohibited = NA_character_)
```

### Promotions

```{r}
promotion <- responses %>% 
    select(c("School.Name", "School.State.Abbreviation"), contains("promotion")) %>% 
    rename(item = !!names(.[3])) %>% 
    separate_rows(item, sep = ", ") %>% 
    mutate(item = trimws(item)) %>% 
    mutate(type = "promotion") %>% 
    mutate(prohibited = NA_character_)
```

### Rationale

```{r}
rationale <- responses %>% 
  select(c(1:6), "Check.any.of.the.following.words.phrases.that.appear.in.the.dress.code.") %>% 
  separate_rows(7, sep = ",") %>% 
  rename(words = Check.any.of.the.following.words.phrases.that.appear.in.the.dress.code.) %>% 
  mutate(words = trimws(words)) %>% 
  rename(item = words) %>% 
  mutate(type = "rationale") %>% 
  select(c("School.Name", "School.State.Abbreviation", "item", "type")) %>% 
  mutate(item = case_when(
    grepl("appropriate", item) ~ "appropriate/inappropriate",
    grepl("clean", item) ~ "clean",
    grepl("interfer", item) ~ "interfere with learning",
    grepl("respect", item) ~ "respect/disrespect",
    grepl("safe", item) ~ "safe/safety", 
    TRUE ~ item
  )) %>% 
  mutate(prohibited = NA_character_)
```


### Combine All

```{r}
allBans <- bannedBySchool %>% 
  bind_rows(promotion, straps, lengthBySchool, rationale)

googledrive::drive_download("manualCorrections", path = here::here("raw_data", "collected", "manualCorrections.csv"), type = "csv", overwrite = TRUE)
  
  manualCorrect <- read.csv(here::here("raw_data", "collected", "manualCorrections.csv"), stringsAsFactors = FALSE, header = TRUE, na.strings = c("", " "))
  
cleanBans <- allBans %>% 
    ungroup() %>% 
    mutate(item = trimws(item)) %>% 
    left_join(manualCorrect) %>% 
    mutate(item = ifelse(!is.na(itemCorrect), itemCorrect, item),
           type = ifelse(!is.na(catCorrect), catCorrect, type)) %>% 
    select(c(School.Name, School.State.Abbreviation, item, type, prohibited))

## If visible undergarments w/ bra was checked, visible undergarments (without bra)
## often wasn't checked. It should have been. This is to correct that error. 
visibleBra <- cleanBans %>% 
  filter(grepl("bras and or bra straps", item)) %>% 
  mutate(item = "visible")

fullCleanBan <- cleanBans %>% 
  rbind(visibleBra) %>% 
  distinct(School.Name, type, item, .keep_all = TRUE)

write.csv(fullCleanBan, here::here("processed_data", "cleaned_bans.csv"), row.names = FALSE)
```

```{r}
cleanByItem <- fullCleanBan %>% 
  group_by(type, item) %>% 
  count(., sort = TRUE)
```


## Outputting Data

Now we need to output some specific types of data for the front-end version of this story. 

First, body part bans. 

### Body Parts

```{r}
body <- fullCleanBan %>% 
  filter(type == "body") %>% 
  distinct(School.Name)

nSchools <- fullCleanBan %>% 
  distinct(School.State.Abbreviation, School.Name)

# Percentage of schools that ban some body part
nrow(body)/nrow(nSchools)

# Percentage of schools that ban specific body parts
bodyPer <- fullCleanBan %>% 
  filter(School.Name %in% body$School.Name) %>% 
  filter(type == "body") %>% 
  count(item, sort = TRUE) %>% 
  mutate(per = n/nrow(nSchools) * 100) %>% 
  mutate(per = round(per, 0)) %>% 
  filter(per >= 5)

write.csv(bodyPer, "../src/assets/data/bodyPer.csv", row.names = FALSE)
```


```{r}
bodyButtons <- c("midsection midriff", "cleavage", "back", "breasts chest", "buttocks", "stomach", "torso")


## Importing NCES data
schoolData <- read.csv(here::here("raw_data", "schools", "elsi.csv"), skip = 6, header = TRUE, na.strings = c("†", "-"), stringsAsFactors = FALSE)

columns <- c("schoolName", "state", "website", "stateAbb", "schoolType", "charterSchool", "magnetSchool", "locale", "totalStudents", "lowestGrade", "highestGrade", "totalRace", "raceNative", "raceAsian", "raceHispanic", "raceBlack", "raceWhite", "raceHawaiian", "raceMultiple", "studentTeacherRatio", "teacherCount")

colnames(schoolData) <- columns

googledrive::drive_download("shuffledHandbooks", path = here::here("raw_data", "collected", "completedHandbooks.csv"), type = "csv", overwrite = TRUE)

completedHandbooks <- read.csv(here::here("raw_data", "collected", "completedHandbooks.csv"), stringsAsFactors = FALSE, header = TRUE)

completedHandbooksClean <- completedHandbooks %>% 
  filter(entered != "",
         !grepl("skip", entered)) %>% 
  select(c(schoolName, stateAbb, locale, totalStudents))

schoolBody <- fullCleanBan %>% 
  filter(School.Name %in% body$School.Name) %>% 
  filter(type == "body",
         item %in% bodyButtons) %>% 
  mutate(item = case_when(
    item == "midsection midriff" ~ "midriff",
    item == "breasts chest" ~ "chest",
    TRUE ~ item 
  ),
  fill = "y") %>% 
  #spread("item", "fill", fill = NA) %>% 
  rename("schoolName" = "School.Name", "state" = "School.State.Abbreviation") %>% 
  right_join(completedHandbooksClean) %>% 
  mutate(totalStudents = as.numeric(totalStudents)) %>% 
  mutate(countGroup = case_when(
    totalStudents < 200 ~ "< 200",
    between(totalStudents, 200, 499) ~ "200-499",
    between(totalStudents, 500, 999) ~ "500-999",
    between(totalStudents, 1000, 1500) ~ "1000-1500",
    totalStudents >= 1500 ~ "1500+",
    TRUE ~ NA_character_
  )) %>% 
  mutate(localeGroup = case_when(
    grepl("Rural", locale) ~ "rural",
    grepl("City", locale) ~ "city", 
    grepl("Suburb", locale) ~ "suburb",
    grepl("Town", locale) ~ "town",
    TRUE ~ NA_character_
  )) %>% 
  mutate(state = trimws(stateAbb)) %>% 
  select(-c("locale", "totalStudents", "stateAbb", "type")) %>%
  mutate(schoolName = gsub("[[:space:]]h s|[[:space:]]hs", " High School", tolower(schoolName)),
         schoolName = toTitleCase(schoolName)) %>% 
  ungroup() %>% 
  group_by(state, schoolName) %>% 
  mutate(bodyParts = list(item)) %>% 
  select(-c("item", "fill")) %>% 
  distinct(state, schoolName, .keep_all = TRUE)

bodyJSON <- jsonlite::toJSON(schoolBody, pretty = TRUE, flatten = TRUE)

write(bodyJSON, "../src/assets/data/bodyPerSchool.json")
```

### Clothes

```{r}
remove <- c("sexually provocative suggestive", "revealing", "dirty", "immodest")

'%notin%' <- Negate('%in%')

items <- fullCleanBan %>% 
  filter(type != "promotion",
         type != "rationale", 
         type != "body",
         type != "footwear",
         type != "headwear", 
         type != "grooming",
         type != "accessories",
         item %notin% remove) %>% 
  mutate(item = case_when(
    grepl("leggings", item) ~ "leggings",
    grepl("bras and or bra straps", item) ~ "visible bra straps",
    TRUE ~ item
  )) %>% 
  mutate(item = trimws(item)) %>% 
  group_by(type, item) %>% 
  count(., sort = TRUE)


googledrive::drive_download("clothes", path = here::here("raw_data", "collected", "clothesDetails.csv"), type = "csv", overwrite = TRUE)
  
manualDetails<- read.csv(here::here("raw_data", "collected", "clothesDetails.csv"), stringsAsFactors = FALSE, header = TRUE, na.strings = c("", " "))

detailedItems <- items %>% 
  left_join(manualDetails) %>%
  filter(!is.na(market),
         !is.na(slug)) %>% 
  ungroup() %>% 
  mutate(per = round(n / nrow(nSchools) * 100, 0)) %>% 
  filter(per >= 5) %>% 
  dplyr::select(c(slug, market, reveal_body, n, per)) %>% 
  mutate(group = per - (per %% 10)) 

write.csv(detailedItems, "../src/assets/data/clothes.csv", row.names = FALSE)
```

```{r}
ruleCounts <- fullCleanBan %>% 
  group_by(School.State.Abbreviation, School.Name) %>% 
  count(.)
```

```{r}
lengthCounts <- length %>% 
  separate_rows(length, sep = ",") %>% 
  group_by(length) %>% 
  count(., sort = TRUE) %>% 
  mutate(per = round(n / nrow(nSchools) * 100, 0))
```


### Words

```{r}
words <- fullCleanBan %>% 
  filter(type == "rationale") %>% 
  group_by(item) %>% 
  count(., sort = TRUE) %>% 
  mutate(per = round(n / nrow(nSchools) * 100, 0)) %>% 
  filter(per >= 10) %>% 
  mutate(display = case_when(
    item == "disruption/distraction" ~ "Distract or Disrupt",
    item == "appropriate/inappropriate" ~ "Appropriate",
    item == "safe/safety" ~ "Safe",
    item == "health" ~ "Health",
    item == "interfere with learning" ~ "Interfere with Learning",
    item == "clean" ~ "Clean",
    item == "modest/modesty" ~ "Modest",
    item == "neat" ~ "Neat",
    item == "respect/disrespect" ~ "Respect",
    item == "good taste" ~ "Good Taste",
    TRUE ~ item
  )) 

write.csv(words, "../src/assets/data/words.csv", row.names = FALSE)
```

```{r}
links <- responses %>% 
  select(2:6) 

linksForRepo <- links %>% 
  rename(schoolName = School.Name, state = School.State.Abbreviation, link = Link.to.Dress.Code, text = Copy.Entire.Dress.Code.Here) %>% 
  select(-Copy.Dress.Code.Justification.Here)

write.csv(linksForRepo, here::here("processed_data", "forRepo", "full_text.csv"), row.names = FALSE)
```

```{r}
ex <- rationale %>% 
  left_join(links) %>% 
  mutate(allText = str_replace_all(Copy.Entire.Dress.Code.Here, "[\r\n\t]" , " "))
```

```{r}
extractWords <- function(word){
  regex <- glue("[^.]*({word})[^.]*\\.")
  
  extractions <- ex %>% 
    filter(grepl(word, item)) %>% 
    mutate(extract = str_extract_all(allText, regex))
}

wordsToExtract <- c("distract", "disrupt", "appropriate", "safe", "health", "interfere", "clean", "modest", "neat", "respect", "taste")

testEx <- extractWords("distract")

extracted <- purrr::map_dfr(wordsToExtract, extractWords)

unlistExtracted <- extracted %>% 
  unnest(extract) %>% 
  select(c(1, 2, 3, 5, 9)) %>% 
  mutate(schoolName = gsub("[[:space:]]h s|[[:space:]]hs", " High School", tolower(School.Name)),
         schoolName = toTitleCase(schoolName)) %>% 
  rename(link = "Link.to.Dress.Code", state = "School.State.Abbreviation") %>% 
  select(schoolName, state, link, item, extract) %>% 
  mutate(item = case_when(
    grepl("appropriate", item) ~ "appropriate/inappropriate",
    grepl("clean", item) ~ "clean",
    grepl("interfer", item) ~ "interfere with learning",
    grepl("respect", item) ~ "respect/disrespect",
    grepl("safe", item) ~ "safe/safety", 
    grepl("taste", item) ~ "good taste",
    TRUE ~ item
  )) %>% 
  distinct(link, item, extract, .keep_all = TRUE) %>%  
  group_by(link, item) %>% 
  arrange(link, item) 

write.csv(unlistExtracted, here::here("processed_data", "extracted_examples.csv"), row.names = FALSE)

## Manually selected one per school
googledrive::drive_download("extracted_examples", path = here::here("processed_data", "extracted_examples_clean.csv"), type = "csv", overwrite = TRUE)
  
manuallyExtracted<- read.csv(here::here("processed_data", "extracted_examples_clean.csv"), stringsAsFactors = FALSE, header = TRUE, na.strings = c("", " "))

shuffled <- manuallyExtracted[sample(nrow(manuallyExtracted)),]

write.csv(shuffled, "../src/assets/data/extract.csv", row.names = FALSE)
```


### Subjective

```{r}
subj <- responses %>% 
  select(!!c(2, 3, 151, 152)) %>% 
  rename(present = 3,
         example = 4) %>% 
  filter(!is.na(present),
         present != "no")

nrow(subj)/nrow(responses)
```

### States

```{r}
states <- responses %>% 
  select(School.State.Abbreviation) %>% 
  mutate(stateAbb = toupper(School.State.Abbreviation)) %>% 
  count(stateAbb, sort = TRUE)
```

Compare to all high schools per state in NCES system

```{r}
schoolData <- read.csv(here::here("raw_data", "schools", "elsi.csv"), skip = 6, header = TRUE, na.strings = c("†", "-"), stringsAsFactors = FALSE)

columns <- c("schoolName", "state", "website", "stateAbb", "schoolType", "charterSchool", "magnetSchool", "locale", "totalStudents", "lowestGrade", "highestGrade", "totalRace", "raceNative", "raceAsian", "raceHispanic", "raceBlack", "raceWhite", "raceHawaiian", "raceMultiple", "studentTeacherRatio", "teacherCount")

colnames(schoolData) <- columns

mappedNames <- setNames(state.abb, state.name)

schoolDataCounts <- schoolData %>% 
  filter(schoolType == "1-Regular school",
         magnetSchool == "2-No",
         charterSchool == "2-No") %>% 
  count(stateAbb, sort = TRUE) %>% 
  mutate(stateAbb = trimws(stateAbb))
```

```{r}
collected <- states %>% 
  left_join(schoolDataCounts, by = "stateAbb") %>% 
  mutate(per = round((n.x / n.y) * 100, 0))
```


## For Repo

```{r}
allBansCleaned <- fullCleanBan %>% 
  rename(schoolName = School.Name, state = School.State.Abbreviation)

nSchools <- allBansCleaned %>% 
  distinct(state, schoolName) %>% 
  count(.)

write.csv(allBansCleaned, here::here("processed_data", "forRepo", "banned_items.csv"), row.names = FALSE)
```

```{r}
write.csv(completedHandbooksClean, here::here("processed_data", "forRepo", "school_metadata.csv"), row.names = FALSE)
```

Code for calculating `body_percentages.csv`

```{r eval=FALSE, include=FALSE}
## Check which schools ban body parts
body <- allBansCleaned %>% 
  filter(type == "body") %>% 
  distinct(schoolName)

# Percentage of schools that ban some body part
nrow(body)/nrow(responses)

# Percentage of schools that ban specific body parts
bodyPercent <- allBansCleaned %>% 
  filter(School.Name %in% body$School.Name) %>% 
  filter(type == "body") %>% 
  count(item, sort = TRUE) %>% 
  mutate(per = n/nSchools$n * 100) %>% 
  mutate(per = round(per, 0)) %>% 
  filter(per >= 5)

write.csv(bodyPercent, here::here("processed_data", "forRepo", "body_percentages.csv"))
```

Code for calculating `body_by_school.json`

```{r eval=FALSE, include=FALSE}
bodyButtons <- c("midsection midriff", "cleavage", "back", "breasts chest", "buttocks", "stomach", "torso")

## Check which schools ban body parts
body <- allBansCleaned %>% 
  filter(type == "body") %>% 
  distinct(schoolName)


bodyBySchool <- allBansCleaned %>% 
  filter(schoolName %in% body$schoolName) %>% 
  filter(type == "body",
         item %in% bodyButtons) %>% 
  mutate(item = case_when(
    item == "midsection midriff" ~ "midriff",
    item == "breasts chest" ~ "chest",
    TRUE ~ item 
  ),
  fill = "y") %>% 
  right_join(completedHandbooksClean) %>% 
  mutate(totalStudents = as.numeric(totalStudents)) %>% 
  mutate(countGroup = case_when(
    totalStudents < 200 ~ "< 200",
    between(totalStudents, 200, 499) ~ "200-499",
    between(totalStudents, 500, 999) ~ "500-999",
    between(totalStudents, 1000, 1500) ~ "1000-1500",
    totalStudents >= 1500 ~ "1500+",
    TRUE ~ NA_character_
  )) %>% 
  mutate(localeGroup = case_when(
    grepl("Rural", locale) ~ "rural",
    grepl("City", locale) ~ "city", 
    grepl("Suburb", locale) ~ "suburb",
    grepl("Town", locale) ~ "town",
    TRUE ~ NA_character_
  )) %>% 
  mutate(state = trimws(stateAbb)) %>% 
  select(-c("locale", "totalStudents", "stateAbb", "type")) %>%
  mutate(schoolName = gsub("[[:space:]]h s|[[:space:]]hs", " High School", tolower(schoolName)),
         schoolName = toTitleCase(schoolName)) %>% 
  ungroup() %>% 
  group_by(state, schoolName) %>% 
  mutate(bodyParts = list(item)) %>% 
  select(-c("item", "fill")) %>% 
  distinct(state, schoolName, .keep_all = TRUE)

bodySchoolJSON <- jsonlite::toJSON(bodyBySchool, pretty = TRUE, flatten = TRUE)

write(bodySchoolJSON, here::here("processed_data", "forRepo", "body_by_school.json"))
```

Code for calculating `clothes_percentages.csv`

```{r eval=FALSE, include=FALSE}
remove <- c("sexually provocative suggestive", "revealing", "dirty", "immodest")

'%notin%' <- Negate('%in%')

clothingItems <- allBansCleaned %>% 
  filter(type != "promotion",
         type != "rationale", 
         type != "body",
         type != "footwear",
         type != "headwear", 
         type != "grooming",
         type != "accessories",
         item %notin% remove) %>% 
  mutate(item = case_when(
    grepl("leggings", item) ~ "leggings",
    grepl("bras and or bra straps", item) ~ "visible bra straps",
    TRUE ~ item
  )) %>% 
  mutate(item = trimws(item)) %>% 
  group_by(type, item) %>% 
  count(., sort = TRUE)


googledrive::drive_download("clothes", path = here::here("processed_data", "forRepo", "clothesDetails.csv"), type = "csv", overwrite = TRUE)
  
clothesDetails<- read.csv(here::here("processed_data", "forRepo", "clothesDetails.csv"), stringsAsFactors = FALSE, header = TRUE, na.strings = c("", " "))

detailedClothingItems <- clothingItems %>% 
  left_join(clothesDetails) %>%
  filter(!is.na(market)) %>% 
  ungroup() %>% 
  mutate(per = round(n / nSchools$n * 100, 0)) %>% 
  filter(per >= 5) %>% 
  dplyr::select(c(slug, market, reveal_body, n, per)) %>% 
  mutate(group = per - (per %% 10)) 

write.csv(detailedClothingItems, here::here("processed_data", "forRepo", "clothes_percentages.csv"), row.names = FALSE)
```

Code for `words_percentages.csv`

```{r eval=FALSE, include=FALSE}
wordsPercentages <- allBansCleaned %>% 
  filter(type == "rationale") %>% 
  group_by(item) %>% 
  count(., sort = TRUE) %>% 
  mutate(percent = round(n / nSchools$n * 100, 0)) %>% 
  filter(percent >= 10) %>% 
  mutate(display = case_when(
    item == "disruption/distraction" ~ "Distract or Disrupt",
    item == "appropriate/inappropriate" ~ "Appropriate",
    item == "safe/safety" ~ "Safe",
    item == "health" ~ "Health",
    item == "interfere with learning" ~ "Interfere with Learning",
    item == "clean" ~ "Clean",
    item == "modest/modesty" ~ "Modest",
    item == "neat" ~ "Neat",
    item == "respect/disrespect" ~ "Respect",
    TRUE ~ item
  )) 

write.csv(wordsPercentages, here::here("processed_data", "forRepo", "words_percentages.csv"), row.names = FALSE)
```

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```


Exporting sanction data

```{r}
sanctions <- responses %>% 
    select(c("School.Name", "School.State.Abbreviation"), contains("sanctions"))

checkedSanctions <- sanctions %>% 
  select(-contains("any.other")) %>% 
  gather(key = sanction, value = offense, colnames(select(., contains("sanctions")))) %>% 
  filter(!is.na(offense)) %>% 
  separate_rows(offense, sep = ", ") %>% 
  mutate(offense = gsub(" Offense", "", offense)) %>% 
  mutate(sanction = str_replace(sanction, "(.*?\\.{2})", ""),
           sanction = gsub("\\.", " ", sanction),
           sanction = trimws(sanction),
         sanction = gsub("item s", "items", sanction))

manualSanctions <- sanctions %>% 
  select(c("School.Name", "School.State.Abbreviation", contains("any.other"))) %>% 
  rename(sanctions = 3) %>% 
  filter(!is.na(sanctions)) %>% 
  separate_rows("sanctions", sep = ", ") %>% 
  separate(sanctions, into = c("sanction", "offense"), sep = ":") %>% 
  mutate(offense = ifelse(offense == "NA" | is.na(offense), "Any", offense)) %>% 
  mutate(offense = gsub(" offense", "", offense, ignore.case = TRUE))

allSanctions <- checkedSanctions %>% 
  rbind(manualSanctions) %>% 
  rename(schoolName = School.Name, state = School.State.Abbreviation)

write.csv(allSanctions, here::here("processed_data", "forRepo", "sanctions.csv"), row.names = FALSE)
  
```

