---
title: "For Presentation"
author: "Amber Thomas"
date: "12/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is this?

This file exists to compile only the pieces of analysis that I need for the final presentation of this work. I will be pulling in R scripts from other files (that were originally tested in the `analysisUpdate.Rmd` file).

As always, I'll load the necessary packages.

```{r}
library(tidyverse)
library(googledrive)
```

And the appropriate R scripts.
```{r}
source(here::here("r_scripts", "download_data.R"))
source(here::here("r_scripts", "length_limits.R"))
source(here::here("r_scripts", "strap_limits.R"))
source(here::here("r_scripts", "promotion_limits.R"))
source(here::here("r_scripts", "other_limits.R"))
source(here::here("r_scripts", "clean_items.R"))
```


## Downloading the data

By running the `download_data.R` file, we automatically downloaded our data and created the dataframe `responses` which is filled with all of our manually-entered dress code data.

## Cleaning the data

### Length restrictions

To find the length restrictions by garment, we can use the `findLength()` and `findLengthByItem()` functions in the `length_limits.R` script. 

```{r}
length <- findLength(responses)
lengthByItem <- findLengthByItem(length)
```

### Strap width restrictions

To find the strap-width restrictions, we can use the `findStrap()` function in the `strap_limits.R` script.

```{r message = FALSE}
straps <- findStraps(responses)
```

### Word or picture promotion

To find the items that are banned based on the words or pictures printed upon them, we'll use the `findPromotions()` function in the `promotion_limits.R` script.

```{r}
promotions <- findPromotions(responses)
```

### Other banned items

Now we can process everything else using the `findBanned()` function in the `other_limits.R` script.

```{r}
bannedBySchool <- findBanned(responses)
bannedByItem <- findBannedByItem(bannedBySchool)
```

### Combining Banned Items

Alright, now to put the promotions, lengths, straps, and other banned items together. 

```{r}
allBans <- bannedByItem %>% 
  bind_rows(promotions, straps, lengthByItem)
```

And now to clean them (using some manual corrections).

```{r}
source(here::here("r_scripts", "clean_items.R"))
cleanBans <- clean_items(allBans)
```



