---
title: "clusters"
author: "Amber Thomas"
date: "1/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is this?

I was curious about whether or not items banned in dress codes were clustered in any way. For instance, if a school dress code bans "crop tops" are they more likely to ban other feminine items as well (spaghetti strap shirts, short shorts etc.)? Same goes for things like "bandanas" - does banning them increase the likelihood that they also banned things like sagging pants, or "disruptive hairstyles"? 

To figure this out, I'm going to use "Market Basket Analysis". 

```{r}
library(tidyverse)
library(here)
library(arules)
library(arulesViz)
```

```{r}
source(here::here("r_scripts", "download_data.R"))
source(here::here("r_scripts", "other_limits.R"))
source(here::here("r_scripts", "length_limits.R"))
```

## Downloading the data

By running the `download_data.R` file, we automatically downloaded our data and created the dataframe `responses` which is filled with all of our manually-entered dress code data.

## Cleaning Data

First, we need to make our very wide data, long. 

```{r}
bannedBySchool <- findBanned(responses) %>% 
  select(c(School.Name, School.State.Abbreviation, item, type))
```

The above data frame does not include things like length restrictions on pants/shorts/skirts, strap width restrictions, and promotion of various types of products/things on shirts. Let's analyze those here: 

### Length Restrictions

```{r}
length <- findLength(responses)
lengthBySchool <- length %>% 
  mutate(type = "length",
         limits = paste0("short ", limits)) %>% 
  rename(item = limits) %>% 
  select(-length)
```

### Strap Restrictions

```{r}
straps <- responses %>% 
  select(c("School.Name", "School.State.Abbreviation"), contains("shirt.straps")) %>% 
    rename(limits = !!names(.[3])) %>% 
    filter(limits != "") %>% 
    # Separate comma delimited list of items
    separate(limits, into = c("limits", "inches"), sep = ",") %>% 
    mutate(limits = trimws(limits)) %>% 
    mutate(item = "narrow straps",
             type = "shirt") %>% 
  select(c("School.Name", "School.State.Abbreviation", "item", "type"))
```

### Promotions

```{r}
promotion <- responses %>% 
    select(c("School.Name", "School.State.Abbreviation"), contains("promotion")) %>% 
    rename(item = !!names(.[3])) %>% 
    separate_rows(item, sep = ", ") %>% 
    mutate(item = trimws(item)) %>% 
    mutate(type = "promotion")
```

### Rationale

```{r}
rationale <- responses %>% 
  select(c(1:6), "Check.any.of.the.following.words.phrases.that.appear.in.the.dress.code.") %>% 
  separate_rows(7, sep = ",") %>% 
  rename(words = Check.any.of.the.following.words.phrases.that.appear.in.the.dress.code.) %>% 
  mutate(words = trimws(words)) %>% 
  rename(item = words) %>% 
  mutate(type = "rationale") %>% 
  select(c("School.Name", "School.State.Abbreviation", "item", "type"))
```


### Combine All

```{r}
allBans <- bannedBySchool %>% 
  bind_rows(promotion, straps, lengthBySchool, rationale)

googledrive::drive_download("manualCorrections", path = here::here("raw_data", "collected", "manualCorrections.csv"), type = "csv", overwrite = TRUE)
  
  manualCorrect <- read.csv(here::here("raw_data", "collected", "manualCorrections.csv"), stringsAsFactors = FALSE, header = TRUE, na.strings = c("", " "))
  
cleanBans <- allBans %>% 
    ungroup() %>% 
    mutate(item = trimws(item)) %>% 
    left_join(manualCorrect) %>% 
    mutate(item = ifelse(!is.na(itemCorrect), itemCorrect, item),
           type = ifelse(!is.na(catCorrect), catCorrect, type)) %>% 
    select(c(School.Name, School.State.Abbreviation, item, type)) %>% 
    distinct(School.Name, type, item, .keep_all = TRUE)

write.csv(cleanBans, here::here("processed_data", "cleaned_bans.csv"), row.names = FALSE)

totalBans <- cleanBans %>% 
  ## Gather all banned items per school into the same cell, comma separated
  mutate(itemCat = paste0(type, "--", item)) %>% 
  select(c(School.Name, itemCat)) %>% 
  group_by(School.Name) %>% 
  mutate(allItems = paste(itemCat, collapse = ",  ")) %>% 
  distinct(School.Name, .keep_all = TRUE) %>% 
  ungroup() %>% 
  select(allItems) 


write.csv(totalBans, here::here("processed_data", "mba_allBans.csv"), row.names = FALSE, quote = FALSE)
```

## Perform Market Basket Analysis

```{r}
transactions <- read.transactions(here::here("processed_data", "mba_allBans.csv"), format = "basket", sep = ",")
```

Let's look at the "transactions":

```{r}
transactions
summary(transactions)
```

Now to generate rules using the APRIORI algorithm. 

```{r}
associationRules <- apriori(transactions, parameter = list(supp = 0.05, conf = 0.8, maxlen = 5))
```
```{r}
inspect(associationRules[1:20])
```

```{r}
bandanaRules <- apriori(transactions, parameter = list(supp = 0.01, conf = 0.8), appearance = list(default="lhs", rhs="headwear--bandanas"))
```

```{r}
inspect(bandanaRules[1:20])
```

```{r}
bandanaSub <- head(bandanaRules, n = 20, by = "confidence")
plot(bandanaSub, method = "graph", engine = "htmlwidget")
```

Let's look at a subset of all of the rules. 
```{r}
sub <- head(associationRules, n = 50, by = "confidence")
```

```{r}
plot(sub, method = "graph", engine = "htmlwidget")
```

```{r}
sub2 <- head(associationRules, n = 50, by = "confidence")
plot(sub2, method="graph", engine = "htmlwidget")
```


Let's take a look at spaghetti strap shirts

```{r}
cropRules <- apriori(transactions, parameter = list(supp = 0.001, conf = 0.5, maxlen = 3), appearance = list(default="rhs", lhs="rationale--respect/disrespect"))
```
```{r}
cropSub <- head(cropRules, n = 20, by = "lift")
plot(cropSub, method = "graph", engine = "htmlwidget")
```

### For Alvin

Alvin asked for two numbers: 

- The % of schools that explicitly ban one of the 7 most popular body parts
- The % of schools that use `appropriate/inappropriate`, `disruption/distraction` or `interfere with learning` in their rationale. 

```{r}
bodyParts <- c("midsection midriff", "cleavage", "breasts chest", "back", "buttocks", "shoulders", "breasts")

bodyPartPer <- cleanBans %>% 
  filter(type == "body") %>% 
  filter(item %in% bodyParts) %>% 
  distinct(School.Name)

nrow(bodyPartPer) / nrow(responses)
```

```{r}
rat <- c("disruption/distraction", "appropriate/inappropriate", "interfere with learning")

ratPer <- cleanBans %>% 
  filter(type == "rationale") %>% 
  filter(item %in% rat) %>% 
  distinct(School.Name)

nrow(ratPer) / nrow(responses)
```

Let's generate a spreadsheet with links and the actual writing of the dress codes
```{r}
links <- responses %>% 
  select(2:6) 

write.csv(links, here::here("processed_data", "links.csv"), row.names = FALSE)
```

```{r}
body <- allBans %>% 
  filter(type == "body") %>% 
  distinct(School.Name)

nrow(body)/nrow(responses)

bodyPer <- cleanBans %>% 
  filter(School.Name %in% body$School.Name) %>% 
  filter(type == "body") %>% 
  count(item, sort = TRUE) %>% 
  mutate(per = n/nrow(responses))

ggplot(head(bodyPer, n = 15), aes(x = reorder(item, n), y = n)) + geom_bar(stat = "identity")
```

```{r}
items <- cleanBans %>% 
  filter(type != "promotion",
         type != "rationale", 
         type != "body",
         type != "footwear",
         type != "headwear", 
         type != "grooming",
         type != "accessories") %>% 
  group_by(type, item) %>% 
  count(., sort = TRUE) %>% 
  filter(n >= (0.02 * nrow(responses))) %>% 
  mutate(per = n / nrow(responses))

write.csv(items, here::here("processed_data", "items.csv"), row.names = FALSE)

googledrive::drive_download("items", path = here::here("raw_data", "collected", "manualItems.csv"), type = "csv", overwrite = TRUE)
  
  manualItems<- read.csv(here::here("raw_data", "collected", "manualItems.csv"), stringsAsFactors = FALSE, header = TRUE, na.strings = c("", " "))
  
manualCounts <- manualItems %>% 
  filter(!is.na(market)) %>% 
  group_by(market, cover) %>% 
  count(., sort = TRUE)

rat <- cleanBans %>% 
  filter(type == "rationale") %>% 
  group_by(item) %>% 
  count(., sort = TRUE) %>% 
  mutate(per = n / nrow(responses))


```


```{r}
respect <- responses %>% 
  filter(str_detect(Copy.Entire.Dress.Code.Here, "appropriate for their body type")) %>% 
  select(c(School.Name, School.State.Abbreviation, Copy.Entire.Dress.Code.Here))
```

