---
title: "NLP"
author: "Amber Thomas"
date: "11/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Up until this point, I had assumed that all of the dress codes would need to be manually processed, but I think I'd like to give Natural Language Processing a try. Specifically with Part of Sentence and chunking analysis (like [this](https://medium.com/greyatom/learning-pos-tagging-chunking-in-nlp-85f7f811a8cb)). 

```{r}
library(tidyverse)
library(reticulate)
use_python('/usr/local/bin/python3', required = TRUE)
spacy <- import("spacy")
nlp <- spacy$load('en')
library(spacyr)
spacy_initialize(python_executable = '/usr/local/bin/python3')

library(udpipe)
udEnglish <- udpipe_download_model(language = "english")
```

## Test Data
Using NLTK

```{r eval = FALSE}
sentence <- "Sleeveless shirts, blouses, and dresses are acceptable as long as the armholes have finished edges and do not expose the torso."
token <- nltk$word_tokenize(sentence)
tagged <- nltk$pos_tag(token)

grammar = ('''NP: {<DT>?<VBD>*<NNS>} # NP''')

chunkParser = nltk.RegexpParser(grammar)

tree = chunkParser.parse(tagged)

for subtree in tree.subtrees():
    print(subtree)
```
Using spacy
```{r}
doc <- nlp('Apple is looking at buying U.K. startup for $1 billion')

for (i in 10:15){
  print(i)
}
```
Using `spacyr` instead of python's `spacy` inside of `reticulate`.
```{r}
txt <- c(d1 = "Sleeveless shirts, blouses, and dresses are acceptable as long as the armholes have finished edges and do not expose the torso.",
         d2 = "Holes in jeans or pants will be permitted only below mid-thigh length. Holes that are ruled potentially disruptive by the principal will not be permitted.")

# process documents and obtain a data.table
parsedtxt <- spacy_parse(txt)
parsedtxt
```
```{r}
parsedtxt <- spacy_parse(txt, dependency = TRUE, nounphrase = TRUE)
```


Trying with `udpipe` R package

```{r}
txt <- c(d1 = "Sleeveless shirts, blouses, and dresses are acceptable as long as the armholes have finished edges and do not expose the torso. ",
         d2 = "tube tops, tank tops, and halter tops are not allowed")
parsedtxt <- udpipe(txt, object = udEnglish)

parsedtxt$phrase_tag <- as_phrasemachine(parsedtxt$upos, type = "upos")

stats <- keywords_phrases(x = parsedtxt$xpos, term = tolower(parsedtxt$token), 
                          pattern = "((JJ.|NN.)*(NN.*))", 
                          is_regex = TRUE, detailed = FALSE)
```

Since I am trying to solve a very specific problem, I may need to analyze this text in a specific way. 
```{r}
parsedtxtAnalyzed <- parsedtxt %>%
  group_by(doc_id, paragraph_id, sentence_id) %>% 
  mutate(nextToken = lead(token, n = 2)) %>% 
  mutate(adjCombo = case_when(
    
  ))
```

